---
title: "Peer-graded Assignment"
runningheader: "Reproducible Templates for Analysis and Dissemination" # only for pdf output
subtitle: "Reproducible Templates for Analysis and Dissemination" # only for html output
author: "Olaf Thelen-Presanis"
date:  "`r Sys.Date()`"
output:
  rmdformats::downcute:
    self_contained: true
    default_style: "dark"
    downcute_theme: "default"
---

```{r setup, include=FALSE}
## Global options
knitr::opts_chunk$set(cache = TRUE)
```

### Preparation

Loading packages used in this assignment. 
```{r prep, echo=TRUE, message=FALSE, warning=FALSE}
library(magrittr)
library(kableExtra)
```

*Note:* the source code of this publication can be found on [GitHub](https://github.com/othelen/CourseraReproducibleAssignment){target="_blank"}

# Summary {#summary}

This is the final, peer-graded assignment for the Coursera MOOC on 'Reproducible Templates for Analysis and Dissemination'.

It contains

\newcommand{\boxedcheckmark}
  {{\ooalign{$\Box$\cr\hidewidth$\checkmark$\hidewidth}}}
  
  - a title $\checkmark$
  
  - My Name as Author  $\checkmark$

  - The Date  $\checkmark$

  - A section of text summarizing the information in your document or slide presentation (keep this between 3-4 sentences) - *which is actually this section* $\checkmark$
  
  - A [bulleted list](#list) of 3 or more items (either numbered or unnumbered) $\checkmark$
  
  -  A [plot](#pressure) of the built-in 'pressure' dataset $\checkmark$
  
  - A [table](#table) of the top 6 rows of the built-in 'cars' dataset $\checkmark$
  
  - Apply a [theme](#design) or style that changes the font, colors, or other formatting instead of the default template. (HINT: Remember to explore the options in the prettydoc, rmdformats, or revealjs packages) $\checkmark$


# Bulleted list {#list}

Poor sleep quality has been linked with the following symptoms:

+ higher levels of negative mood

+ physical symptoms such as insomnia

+ stress

+ use of medications

+ persistent psychological distress (Glozier et al., 2010; Lund et al., 2010)

*Source:* [APA Style Website](https://apastyle.apa.org/style-grammar-guidelines/lists/bulleted)  

<a href="#summary">back to top</a>

# Pressure Data Set {#pressure}

```{r plot}
plot(pressure, xlab = "Temperature (deg C)",
     ylab = "Pressure (mm of Hg)",
     main = "pressure data: Vapor Pressure of Mercury")
```

<a href="#summary">back to top</a>

# Top rows of the `cars` dataset {#table}

```{r table}
knitr:: kable(head(cars),
              caption = "Top 6 rows of cars dataset") %>%
  kable_styling(full_width = F)
```

<a href="#summary">back to top</a>


# Change of design {#design}

As described by (Xie et al. 2021), useful templates come in various packages. One is the **rmdformats** package (Barnier 2021), which "provides a number of templates that pass different custom styling functions to the output option" ^[Xie et al. 2021, Chapter 16.8.1].

I am using the *downcute* template with the following `YAML header` settings:

```
output:
  rmdformats::downcute:
    self_contained: true
    default_style: "dark"
    downcute_theme: "default"
```

<a href="#summary">back to top</a>

# References {#references}
Barnier, Julien. 2021. Rmdformats: HTML Output Formats and Templates for Rmarkdown Documents.   <https://github.com/juba/rmdformats>{target="_blank"}.  
Yihui Xie, Christophe Dervieux, Emily Riederer. 2021. R Markdown Cookbook.  
<https://bookdown.org/yihui/rmarkdown-cookbook/>{target="_blank"}